Reducing Acceptance Marks in Emerson-Lei Automata by QBF Solving

### 2023-03-17 paper/main.tex
verze pro prvni submission na sat 2023

\newcommand{\Nset}{{\mathbb{N}_0}}
\newcommand{\todo}[1]{\marginpar{\textcolor{red}{#1}}}
%\def\Inf{\ensuremath{\mathsf{Inf}}}
%\def\Fin{\ensuremath{\mathsf{Fin}}}
\DeclareMathOperator{\Inf}{\mathsf{Inf}}
\DeclareMathOperator{\Fin}{\mathsf{Fin}}
\newcommand{\minf}{\mathit{inf}}
\newcommand{\mks}{\mathit{mks}}
%\newcommand{\oM}{\widehat{M}}
\newcommand{\oM}{N}
\newcommand{\rem}{\mathit{nm}}
\newcommand{\mcycle}{\mathit{cycle}}
\newcommand{\msat}{\mathit{satisfies}}
\newcommand{\Te}{T_{\vec{e}}}
% \newcommand{\pre}{{\leftarrow\!\!S}}
% \newcommand{\post}{{S\!\!\rightarrow}}
\newcommand{\pre}{{S_\mathit{pre}}}
\newcommand{\post}{{S_\mathit{post}}}
\def\false{\mathit{false}}
\def\true{\mathit{true}}
\newcommand{\mA}{\mathcal{A}}
\newcommand{\mB}{\mathcal{B}}

@@

\todo{Sem nebo za tu dalsi subsection strcity analyzu slozitosti.}

@@

\begin{table}[b]
\caption{LTL to automata translators used for the experimental evaluation
and the number of successfully translated formulas.}
\label{tab:ltltranslators}
\centering
% \begin{tabular}{lr@{~~~~~~}lr}
% \toprule
% tool        & version&homepage & ~~~automata \\
% \midrule
% \texttt{ltl2dela}~~~ & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 129\\
% \texttt{ltl2dgra} & 21.0 & & 234\\
% \texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 70\\
% \texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 91\\
% \bottomrule
% \end{tabular}
%
\begin{tabular}{lrlrrr}
  \toprule
  &&&& \multicolumn{2}{c}{automata with} \\ \cmidrule(lr){5-6}
  tool &\!\!\!version&homepage & T/O & 0--1 mark & \textbf{2+ marks}\\
  \midrule
  \texttt{ltl2dela} & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}}
       & ? & ? & \textbf{129} \\
  \texttt{ltl2dgra} & 21.0 &
       & ? & ? & \textbf{234}\\
  \texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr}
       & ? & ? & \textbf{70}\\
  \texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela}
       & ? & ? & \textbf{91}\\
  \bottomrule
\end{tabular}
\end{table}

For each automata set (that is, the automata produced by an individual
LTL translator), we have applied all single-level reductions and the
multi-level reduction, always with incremental approach and without
reducing of the number of cubes.
\todo{Vysvetlit, proc neredukujeme cubes?}
The timeout for each QBF query was set to 30 seconds.
%
All reductions have been performed by the tool \texttt{telatko}
built with Spot library version 2.10.4 and Z3 version 4.8.15. The
experiments have been run on a computer with Intel$^\text{®}$ Core™ i7-8700
processor and 32 GB of memory running Ubuntu 20.04.4. We used the tool
\texttt{autcross} of the Spot library to get the statistics of the
reduced automata and the running times.

@@

\todo{popisek Fig. 3 neni hezky. Je to wall time nebo CPU time?}
\begin{figure}[b!]
  \caption{Performance of \telatko on different automata sets. The $x$
    axis represents the number of automata that are processed by
    telatko in the time shown on the $y$ axis.}
\label{fig:quantile}
\bigskip
\centering
\input{quantile.tex}
\end{figure}

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrvnat}
\bibliography{mc}

>>>>

\newcommand{\Nset}{{\mathbb{N}_0}}
\newcommand{\todo}[1]{\marginpar{\textcolor{red}{#1}}}
%\newcommand{\todo}[1]{}
%\def\Inf{\ensuremath{\mathsf{Inf}}}
%\def\Fin{\ensuremath{\mathsf{Fin}}}
\DeclareMathOperator{\Inf}{\mathsf{Inf}}
\DeclareMathOperator{\Fin}{\mathsf{Fin}}
\newcommand{\minf}{\mathit{inf}}
\newcommand{\mks}{\mathit{mks}}
%\newcommand{\oM}{\widehat{M}}
\newcommand{\oM}{N}
\newcommand{\rem}{\mathit{nm}}
\newcommand{\mcycle}{\mathit{cycle}}
\newcommand{\msat}{\mathit{satisfies}}
\newcommand{\Te}{T_{\vec{e}}}
% \newcommand{\pre}{{\leftarrow\!\!S}}
% \newcommand{\post}{{S\!\!\rightarrow}}
\newcommand{\pre}{{S_\mathit{pre}}}
\newcommand{\post}{{S_\mathit{post}}}
\def\false{\mathit{false}}
\def\true{\mathit{true}}
\newcommand{\mA}{\mathcal{A}}
\newcommand{\mB}{\mathcal{B}}

@@

\todo{Sem nebo za tu dalsi subsection strcit analyzu slozitosti.}

@@

\begin{table}[b]
\caption{LTL to automata translators used for the experimental evaluation
and the number of successfully translated formulas.}
\label{tab:ltltranslators}
\centering
\begin{tabular}{lr@{~~~~~~}lr}
\toprule
tool        & version&homepage & ~~~automata \\
\midrule
\texttt{ltl2dela}~~~ & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 129\\
\texttt{ltl2dgra} & 21.0 & & 234\\
\texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 70\\
\texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 91\\
\bottomrule
\end{tabular}
%
% \begin{tabular}{lrlrrr}
%   \toprule
%   &&&& \multicolumn{2}{c}{automata with} \\ \cmidrule(lr){5-6}
%   tool &\!\!\!version&homepage & T/O & 0--1 mark & \textbf{2+ marks}\\
%   \midrule
%   \texttt{ltl2dela} & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}}
%        & ? & ? & \textbf{129} \\
%   \texttt{ltl2dgra} & 21.0 &
%        & ? & ? & \textbf{234}\\
%   \texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr}
%        & ? & ? & \textbf{70}\\
%   \texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela}
%        & ? & ? & \textbf{91}\\
%   \bottomrule
% \end{tabular}
\end{table}

For each automata set (that is, the automata produced by an individual
LTL translator), we have applied all single-level reductions and the
multi-level reduction, always with incremental approach and without
reducing of the number of cubes.
\todo{Vysvetlit, proc neredukujeme pocet cubes?}
The timeout for each QBF query was set to 30 seconds.
%
All reductions have been performed by the tool \texttt{telatko}
built with Spot library version 2.10.4 and Z3 version 4.8.15. The
experiments have been run on a computer with Intel$^\text{®}$ Core™ i7-8700
processor and 32 GB of memory running Ubuntu 20.04.4. We used the tool
\texttt{autcross} of the Spot library to get the statistics of the
reduced automata and the running times.

@@

\todo{popisek Fig. 3 neni hezky. Je to wall time nebo CPU time? Je to
  kumulovany cas nebo pro kazdy automat zvlast? Zmenit popisky os v
  obrazku?}
\begin{figure}[b!]
  \caption{Performance of \telatko on different automata sets. The $x$
    axis represents the number of automata from each automata
    set that are processed by \telatko in the time shown on the $y$
    axis.}
\label{fig:quantile}
\bigskip
\centering
\input{quantile.tex}
\end{figure}

@@

%\bibliographystyle{abbrvnat}
\bibliography{mc}
